Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-03-09 paper/SupMat.Rnw
finished editing through Results

Combining the decompositions of $\olr_{i \bs i}$ and $\olr_{j \bs i}$ and assuming without loss of generality that $\mu_i \leq \mu_j$ so that
species $i$ is the weaker competitor and $\olr_{i \bs i}-q_{ij}\olr_{j \bs i}$ can be regarded as a coexistence metric, we have
\begin{equation}
\olr_{i \bs i}-q_{ij}\olr_{j \bs i}=\Delta_i^0+\Delta_i^E+\Delta_i^C+\Delta_i^{(E\shp C)}+\Delta_i^{[E \nat C]}+\Delta_i^{[EC]},\label{eq:decomp_overall_delta}
\end{equation}
where $\Delta_i^0=\epsilon_i^0- q_{ij} \epsilon_j^0$;
$\Delta_i^E=\olep_i^E -q_{ij}\olep_j^E$ is the contribution to coexistence of environmental variation;
$\Delta_i^C=\olep_i^C -q_{ij}\olep_j^C$ is the contribution to coexistence of variation in competitive pressure;
$\Delta_i^{(E\shp C)}=\olep_i^{(E\shp C)} - q_{ij}\olep_j^{(E\shp C)}$ is the contribution to coexistence of 
variation \emph{per se} in both environment and competition, not including the effects of covariation of these quantities;
 $\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}$is the contribution to coexistence of $EC$ covariation \emph{per se},
not including the effects of asymmetric tail associations between environment and competition;
and $\Delta_i^{[EC]}=\olep_i^{[EC]} - q_{ij} \olep_j^{[EC]}$ is the contribution to coexistence of 
asymmetric tail associations. The subscript $i$ on all these newly defined quantities $\Delta_i$ refers to species $i$.

@@

\section{Decomposing storage effects in the diatom case study}\label{sect:Empircal_app}

@@

\section{\emph{Cyclotella psedosteligera} as the invader}\label{sect:Invader2}
We generated plots analougous to Fig. \ref{MT-fig:fig5} and Fig. \ref{MT-fig:fig6} for the reverse invader-resident scenario where \emph{C. pseudosteligera} is the invader and \emph{F. crotonensis} is the resisent to compute the IGR and decompose coexistence mechanisms of \emph{C. pseudosteligera}. Fig. \ref{fig:fig5_2} is analogous to Fig. \ref{MT-fig:fig5} and shows changes in the IGR and decomposed mechanisms in response to change in one temperature parameter while the other two are held constant. Within the parameters of our simulations, the IGR of \emph{C. pseudosteligera}

>>>>

Combining the decompositions of $\olr_{i \bs i}$ and $\olr_{j \bs i}$, we have
\begin{equation}
\olr_{i \bs i}-q_{ij}\olr_{j \bs i}=\Delta_i^0+\Delta_i^E+\Delta_i^C+\Delta_i^{(E\shp C)}+\Delta_i^{[E \nat C]}+\Delta_i^{[EC]},\label{eq:decomp_overall_delta}
\end{equation}
where $\Delta_i^0=\epsilon_i^0- q_{ij} \epsilon_j^0$;
$\Delta_i^E=\olep_i^E -q_{ij}\olep_j^E$ is the contribution to coexistence of environmental variation;
$\Delta_i^C=\olep_i^C -q_{ij}\olep_j^C$ is the contribution to coexistence of variation in competitive pressure;
$\Delta_i^{(E\shp C)}=\olep_i^{(E\shp C)} - q_{ij}\olep_j^{(E\shp C)}$ is the contribution to coexistence of 
variation \emph{per se} in both environment and competition, not including the effects of covariation of these quantities;
 $\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}$is the contribution to coexistence of $EC$ covariation \emph{per se},
not including the effects of asymmetric tail associations between environment and competition;
and $\Delta_i^{[EC]}=\olep_i^{[EC]} - q_{ij} \olep_j^{[EC]}$ is the contribution to coexistence of 
asymmetric tail associations. The subscript $i$ on all these newly defined quantities $\Delta_i$ refers to species $i$.

@@

\section{     Decomposing storage effects in the diatom case study}\label{sect:Empircal_app}

@@

\section{     \emph{Cyclotella psedosteligera} as the invader}\label{sect:Invader2}
We generated plots analougous to Fig. \ref{MT-fig:fig5} and Fig. \ref{MT-fig:fig6} for the reverse invader-resident scenario where \emph{C. pseudosteligera} is the invader and \emph{F. crotonensis} is the resisent to compute the IGR and decompose coexistence mechanisms of \emph{C. pseudosteligera}. Fig. \ref{fig:fig5_2} is analogous to Fig. \ref{MT-fig:fig5} and shows changes in the IGR and decomposed mechanisms in response to change in one temperature parameter while the other two are held constant. Within the parameters of our simulations, the IGR of \emph{C. pseudosteligera}
